\pkg{hesim}: Health Economic Simulation Modeling and Decision Analysis

### 2021-02-25 manuscript.Rnw
Minor code styling edit

<<psm_fits_soc>>=
onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
fit_pfs_soc_wei <- flexsurv::flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female,
  data = onc_pfs_os_soc,
  dist = "weibull")

>>>>

<<psm_fits_soc>>=
onc_pfs_os_soc <- onc_pfs_os[strategy_name == "SOC"]
fit_pfs_soc_wei <- flexsurvreg(
  Surv(pfs_time, pfs_status) ~ female,
  data = onc_pfs_os_soc,
  dist = "weibull")
